%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {RACWA} % Organization
    {Perth, WA, Australia} % Location
    {April 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Spearheaded the development of a new self-service capability within the myRAC portal, allowing members to instantly manage their Roadside Assistance cover online. This initiative automated \textbf{~3,700 annual member requests, directly improving operational efficiency} and member satisfaction.}
        \item {\textbf{Engineered a high-adoption digital membership card feature, achieving a 96\% member uptake rate within three months of launch.} Led the end-to-end development, including threat modelling and security architecture, to allow members to securely add their RAC card to their digital wallets.}
        \item {\textbf{Led the strategic replacement of the RAC website's Azure Search with a vendor-hosted Solr solution.} This migration significantly enhanced search performance and speed (cutting the search time by half), improving content discoverability and the overall user experience on the main site.}
        \item {\textbf{Drove the evolution of the myRAC digital platform through a major re-platforming and redesign.} Led the technical migration of the Next.js front-end, GraphQL layer, and back-end services into a unified monorepo, while simultaneously implementing a complete UX redesign with new navigation and back-end integrations.}
        \item {\textbf{Enhanced the Autoservice booking platform by leading the integration of a third-party vehicle registration look-up service.} This involved full-stack development of front-end workflows and back-end APIs to streamline the booking process and reduce data entry, resulting in \textbf{a significant reduction in member drop-off rates during the journey.}}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Innovation Engineer (Promoted from Software Engineer)} % Job title (Consolidated for the entire Fugro period)
    {Fugro Marine Australia} % Organization
    {Perth, WA, Australia} % Location
    {June 2006 - March 2022} % Date(s) - Consolidated full tenure
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Architected and delivered a low-latency (6s) real-time video streaming platform} for remote ROV seabed pipeline inspections, leveraging \textbf{AWS Elemental (MediaLive, MediaStore), CloudFront (signed cookies), React/Material UI, and a TypeScript/DynamoDB user management backend}. Spearheaded CI/CD automation via AWS CDK.}
          \begin{itemize}
            \item {Engineered the complete user experience, developing the video streaming front-end (React, Material UI) and a full-stack administration system for client channel and user management.}
            \item {Architected the core cloud infrastructure using AWS Elemental MediaLive and built a fully automated CI/CD deployment pipeline with AWS CDK, ensuring scalable and reliable delivery.}
          \end{itemize}
        \item {\textbf{Cloud \& Full-Stack Development:} Architected and deployed a variety of scalable systems on AWS, including a data exchange for Uncrewed Surface Vessels (USVs) and a marine vessel reporting website. Leveraged a broad range of technologies including .NET Core, TypeScript, Docker, and AWS services (Lambda, ECS/Fargate, S3, DynamoDB).}
        \item {\textbf{DevOps \& Infrastructure Automation:} Established and maintained robust CI/CD pipelines across multiple projects using Jenkins and GitHub Actions. Championed Infrastructure as Code (IaC) with Terraform and CloudFormation to ensure rapid, reliable, and repeatable deployments.}
        \item {\textbf{Data Processing \& Machine Learning:} Contributed to a cloud-hosted Machine Learning system for the automated classification of multibeam sonar data. Streamlined and automated complex data processing workflows for vessel-based pipe inspections, significantly reducing manual effort.}
        \item {\textbf{System Modernisation \& Core Systems:} Led a team in refactoring monolithic applications into a Service-Oriented Architecture (SOA), enhancing scalability. Architected and maintained core modules for Fugro's next-generation global data acquisition software suite using .NET and WPF.}
        \item {\textbf{Foundational Engineering:} Built a strong career foundation as a junior engineer, contributing to all the aspects of the in-house survey software suite, including data acquisition, processing, and visualisation using C++, MFC, and C\#.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}

